## Load the libraries

To run RSelenium, the Java Development Kit (JDK) must be installed first

-   [Installation Tutorial for Windows](https://www.youtube.com/watch?v=IJ-PJbvJBGs&t=3s&ab_channel=ProgrammingKnowledge)

-   [Installation Tutorial for MacOS](https://www.youtube.com/watch?v=pxi3iIy4F5A&ab_channel=ProgrammingKnowledge)

```{r}
library(tidyverse)
library(RSelenium)
```

## Create Selenium Driver object

here's how to run it in Chrome

1.  Determine Chrome version by typing [**chrome://version**](chrome://version){.uri} in Chrome address bar

2.  Take note of the digits before the first period (either 2 or 3 digits depending on version)

3.  run binman::list_versions("chromedriver")

4.  Find the version that has the same matching first numbers (in my case, my first digits are 107)

5.  Run the following code. Change the chromever parameter to what matches your version

```{r}
rs_driver_object <- rsDriver(browser = "chrome", chromever = "107.0.5304.62")
```

You can also run this via firefox (which is simpler)

code: ***rs_driver_object \<- rsDriver(browser = "firefox")***

## Access the client object

```{r}
remDr <- rs_driver_object$client
```

## Start the browser

```{r}
remDr$open()
```

## Create an empty data frame to append the data to

```{r}
all_reviews <- data.frame(Professor_ID = NA,
                          Professor_Name = NA,
                          University = NA,
                          Department = NA,
                          Quality = NA,
                          Difficulty = NA,
                          Emotion = NA, 
                          Class_Name = NA, 
                          Comment = NA, Thumbs_Up = NA,
                          Thumbs_Down = NA,
                          Review_Date = NA)
```

## Navigate to the list of the professors

```{r}
remDr$navigate("https://www.ratemyprofessors.com/search/teachers?query=*&sid=1452")
```

## Click on the Close button

```{r}
remDr$findElement(using = "xpath", "//div[starts-with(@class, 'FullPageModal__')]//button")$clickElement()
```

## Close the ad

```{r}
remDr$findElement(using = "xpath", "//a[@id='bx-close-inside-1177612']")$clickElement()
```

## Navigate to a professor's rating

```{r}
remDr$navigate("https://www.ratemyprofessors.com/professor?tid=9310")
```

## Click the "Load More Ratings" button to show all reviews

```{r}
# find number of ratings 
num_of_ratings <- remDr$findElement(using = 'xpath', "//a[@href='#ratingsList']")$getElementText() %>% 
  unlist() %>% 
  str_extract("[:digit:]+") %>% 
  as.numeric()

# determine how many times to click the "Load More Ratings" button
num_of_iterations <- ceiling( (num_of_ratings - 20) / 10)

if (num_of_iterations > 1) { 
  for (i in 1:num_of_iterations) {
    # click to load more ratings
    load_more <- remDr$findElement(using = "xpath", "//button[text()='Load More Ratings']")
    y_position <- load_more$getElementLocation()$y - 100 # determine y position of element - 100
    remDr$executeScript(sprintf("window.scrollTo(0, %f)", y_position)) # scroll to the element
    load_more$clickElement() # click the element
    Sys.sleep(1.5) # pause code for one and half seconds
  }
}
```

## Extract Professor ID, Name, Department, & University

```{r}
# get teacher ID 
professor_id <- remDr$getCurrentUrl() %>% 
  unlist() %>% 
  str_extract("[:digit:]+$")

# find teacher name 
professor_name <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Name')]")$getElementText() %>%
  unlist()

# department 
department <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Title')]//span//b")$getElementText() %>% 
  unlist()

# university 
university <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Title')]//a")$getElementText() %>%
  unlist()
```

## Locate the rating body using xpath

![[Credit: Tech Altum Tutorial](https://tutorial.techaltum.com/htmlTags.html)](https://tutorial.techaltum.com/images/element.png){width="749"}

![[Credit: Guru99](https://www.guru99.com/xpath-selenium.html)](https://www.guru99.com/images/3-2016/032816_0758_XPathinSele1.png){width="750"}

To learn more about how xpath works, you can refer to my [in-depth tutorial on RSelenium](https://www.youtube.com/watch?v=U1BrIPmhx10&t=567s&ab_channel=SamerHijjazi) and the [W3Schools](https://www.w3schools.com/xml/xpath_intro.asp) page.

```{r}
rating_body <- remDr$findElements(using = 'xpath', "//div[starts-with(@class, 'Rating__RatingBody')]")
```

## Collect review function

```{r}
collect_review <- function(rating) { 

  quality <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class, 'CardNumRating')])[3]")$getElementText() %>% 
    unlist() %>% 
    as.numeric()
  
  difficulty <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class, 'CardNumRating')])[6]")$getElementText() %>%
    unlist() %>%
    as.numeric()
  
  emotion <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class, 'EmotionLabel')])[2]")$getElementText() %>%
    unlist()
  
  class_name <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class,'RatingHeader__StyledClass')])[2]")$getElementText() %>% 
    unlist()
  
  comment <- rating$findChildElement(using = "xpath", ".//div[starts-with(@class, 'Comments__StyledComments')]")$getElementText() %>% 
    unlist()
  
  thumbs_up <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class, 'Thumbs__HelpTotal')])[1]")$getElementText() %>% 
    unlist() %>% 
    as.numeric()
  
  thumbs_down <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class, 'Thumbs__HelpTotal')])[2]")$getElementText() %>% 
    unlist() %>% 
    as.numeric()
  
  review_date <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class, 'TimeStamp')])[2]")$getElementText() %>% 
    unlist()
  
  return(list(Professor_ID = professor_id,
              Professor_Name = professor_name, 
              University = university, 
              Department = department,
              Quality = quality, 
              Difficulty = difficulty, 
              Emotion = emotion,
              Class_Name = class_name, 
              Comment = comment, 
              Thumbs_Up = thumbs_up,
              Thumbs_Down = thumbs_down, 
              Review_Date = review_date)) 
}
```

## Apply function to all reviews and append to *all_reviews* dataframe

```{r}
# run the function on all reviews 
reviews <- rating_body %>% map_dfr(~collect_review(.))

# append the reviews to the main dataframe 
all_reviews <- bind_rows(all_reviews, reviews)
```

# **Running the entire program**

## Loop to click on the "Show More" button

```{r}
# initialize empty dataframe
all_reviews <- data.frame(Professor_ID = NA,
                          Professor_Name = NA,
                          University = NA,
                          Department = NA,
                          Quality = NA,
                          Difficulty = NA,
                          Emotion = NA, 
                          Class_Name = NA, 
                          Comment = NA, Thumbs_Up = NA,
                          Thumbs_Down = NA,
                          Review_Date = NA)

# return to main page
remDr$navigate("https://www.ratemyprofessors.com/search/teachers?query=*&sid=1452")
```

## Loop to click on "show more" professors

```{r}
for (t in 1:10) {
  show_more <- remDr$findElement(using = "xpath", "//button[text()='Show More']")
  y_position <- show_more$getElementLocation()$y - 100
  remDr$executeScript(sprintf("window.scrollTo(0, %f)", y_position))  
  show_more$clickElement()
  Sys.sleep(1.5) 
}
```

## Locate teacher card

```{r}
# locates all teacher cards displayed
teacher_cards <- remDr$findElements(using = "xpath", "//a[starts-with(@class, 'TeacherCard__StyledTeacherCard')]")

# extracts urls from teacher cards. We will need these URLs to loop over the data.
teacher_urls <- map(teacher_cards, ~.$getElementAttribute("href") %>% unlist())
```

## The main loop which loops through the professors and collects all their reviews

```{r}
for (t_url in teacher_urls) {

  # navigate to professor's page
  remDr$navigate(t_url)
  
  # a check for skipping over professors with no ratings
  rating_check <- remDr$findElement(using = "xpath", "//div[starts-with(@class,'RatingValue__NumRatings')]")$getElementText() %>% 
    unlist()
  if (rating_check == "No ratings yet. Add a rating.") { next }
  
  #get teacher ID 
  professor_id <- remDr$getCurrentUrl() %>% 
    unlist() %>% 
    str_extract("[:digit:]+$")
  
  # find teacher name 
  professor_name <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Name')]")$getElementText() %>% 
    unlist()
  
  # department 
  department <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Title')]//span//b")$getElementText() %>% 
    unlist()
  
  # university 
  university <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Title')]//a")$getElementText() %>%
    unlist()
  
  # find number of ratings 
  num_of_ratings <- remDr$findElement(using = 'xpath', "//a[@href='#ratingsList']")$getElementText() %>% 
    unlist() %>% 
    str_extract("[:digit:]+") %>% 
    as.numeric()
  
  # determine how many times to click the "Load More Ratings" button
  num_of_iterations <- ceiling((num_of_ratings - 20) / 10)
  
  if (num_of_iterations > 1) { 
    for (i in 1:num_of_iterations) {
      # click to load more ratings
      load_more <- remDr$findElement(using = "xpath", "//button[text()='Load More Ratings']")
      
      y_position <- load_more$getElementLocation()$y - 100 # determine y position of element - 100
      remDr$executeScript(sprintf("window.scrollTo(0, %f)", y_position)) # scroll to the element
      load_more$clickElement() # click the element
      Sys.sleep(1) # pause code for one second
    }
  }
  
  # locate the rating body 
  rating_body <- remDr$findElements(using = 'xpath', "//div[starts-with( @class, 'Rating__RatingBody')]")
  
  # run the function on all reviews 
  reviews <- rating_body %>% map_dfr(~collect_review(.))
  
  # append the reviews to the main dataframe 
  all_reviews <- bind_rows(all_reviews, reviews)
  
  # five second pause before it moves to the next professor 
  Sys.sleep(5)
}
```

## View the data

```{r}
all_reviews %>% as_tibble()
```

## Remove first row of NAs

```{r}
all_reviews <- slice(all_reviews, -1)
```

## Cleaning the emotion column

```{r}
all_reviews$Emotion <- all_reviews$Emotion %>% str_extract("[A-Z]+")
```

## Writing the dataset to a file

```{r}
write_csv(all_reviews, "Rate My Professors Reviews.csv")
```

## Terminate the selenium server

```{r}
system("taskkill /im java.exe /f")
```
